Deep Gaussian Processes and Hierarchical Modeling with Functional Data: A Case Study in Cosmological Power Spectra

### 2024-08-26 paper/main.tex
update sims plots' palette and layout

Here, we provide results from a simulation study comparing the GP and DGP models, in which case the true curve is known. Following \cite{moran2024dpc}, we consider two functions (1 and 2) each with three variance specifications (settings ``A", ``B", ``C"). Our mean squared error (MSE) results are seen in Figure \ref{fig:collect_sims}; our DGP-HM model outperforms these current benchmark methods. \textcolor{blue}{We can also include a setting ``D", where the underlying error covariance has spatial dependence (e.g., noise with a Mat'ern covariance). Additionally, we can look at linear theory simulations.}

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{collect_sims.png}
    \caption{Average MSE of our method across all $k$ values. \textcolor{blue}{Add competitors.}}
    \label{fig:collect_sims}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{rmse_box.png}
    \caption{Boxplot of all RMSEs of each method across all six test models. From top to bottom: box plots for our training method, process convolution training method, Cosmic EMU predictions, and our DGP-PC predictions.}
    \label{fig:plot_rmse_box}
\end{figure}

>>>>

Here, we provide results from a simulation study comparing the GP and DGP models, in which case the true curve is known. Following \cite{moran2024dpc}, we consider two functions (1 and 2) each with three variance specifications (settings ``A", ``B", ``C"). Our mean squared error (MSE) results are seen in Figure \ref{fig:sims_MSE}; our DGP-HM model outperforms these current benchmark methods. \textcolor{blue}{We can also include a setting ``D", where the underlying error covariance has spatial dependence (e.g., noise with a Mat'ern covariance). Additionally, we can look at linear theory simulations.}

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{sims_logS.png}
    \caption{Boxplot of log scores across two different functions and covariance settings (lower is better). For each case, twenty random batches were simulated.}
    \label{fig:sims_logS}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=6in]{sims_MSE.png}
    \caption{Boxplot of MSEs across two different functions and covariance settings (lower is better). For each case, twenty random batches were simulated.}    \label{fig:sims_MSE}
\end{figure}

@@

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=6in]{rmse_box.png}
%     \caption{Boxplot of all RMSEs of each method across all six test models. From top to bottom: box plots for our training method, process convolution training method, Cosmic EMU predictions, and our DGP-PC predictions.}
%     \label{fig:plot_rmse_box}
% \end{figure}
